# Introduction {#intro}

Muitas vezes, é de nosso interesse comparar parâmetros entre grupos.

Creating sequence of dates. Simulated values will be regarded to a weekly period of time.

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
# sequence of dates (weekly)
date_seq <- seq.Date(from = as.Date("2022-01-01"),
                     to = as.Date("2022-06-30"),
                     by = "week")
# number of weeks
n_week <- length(date_seq)
```

Simulating data-set with poisson and negative binomial distributions.
(explicar parametros e o que os valores da tabela significam. abc)
```{r nice-tab}
sim_data <- data.frame(
  week = date_seq,
  poisson = rpois(n = n_week, lambda = 15),
  neg_bin = rnbinom(n = n_week, mu = 10, size = 4)
)

knitr::kable(
  head(sim_data, 10), caption = "Simulated values",
  booktabs = TRUE)
```

Explaining the difference between distributions.

```{r nice-fig, warning=FALSE, fig.width=7, echo=FALSE}
library(ggh4x)
library(patchwork)

p1 <- ggplot(
  data.frame(x = 0:30, y = dpois(0:30, lambda = 5))
) +
  geom_point(
    aes(x = x, y = y),
    colour = "#E41A1C"
  ) +
  geom_segment(
    aes(x = x, xend = x, y = 0, yend = y),
    colour = "#E41A1C", alpha = 0.5
  ) +
  labs(
    x = "", y = "",
    title = "Poisson \u03BB = 5"
  ) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

p2 <- ggplot(
  data.frame(x = 0:30, y = dnbinom(0:30, mu = 10, size = 4))
) +
  geom_point(
    aes(x = x, y = y),
    colour = "#377EB8"
  ) +
  geom_segment(
    aes(x = x, xend = x, y = 0, yend = y),
    colour = "#377EB8", alpha = 0.5
  ) +
  labs(
    x = "", y = "",
    title = "Negative Binomial"
  ) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

p3 <- p1 / p2

p3
```
Now we are going to use this values to simulate $n$ observations for a continuous distribution and sum them up.
This will be our simulated severity loss.
Gamma, Log-normal and Weibull.

Customized function.


```{r}
severidade <- function(n_dist, dist, pars) {

  random_function <- switch(dist,
    gamma     = "rgamma",
    lognormal = "rlnorm",
    weibull   = "rweibull",
    stop("Invalid distribution")
  )

  parameters <- c("n" = n_dist, pars)
  values <- do.call(what = random_function, args = parameters)

  return(sum(values))
}
```

Severity values with frquency genreated by poisson distribution
```{r}

sev_pois <- sim_data %>%
  select(week, poisson) %>%
  dplyr::rowwise() %>%
  mutate(
    # gamma
    gamma = severidade(
      n_dist = poisson, dist = "gamma",
      pars = list("shape" = 6, "rate" = 0.0006)
    ),
    # log-normal
    lnorm = severidade(
      n_dist = poisson, dist = "lognormal",
      pars = list("meanlog" = 9, "sdlog" = 0.4)
    ),
    # weibull
    weib = severidade(
      n_dist = poisson, dist = "weibull",
      pars = list("shape" = 2.75, "scale" = 12000)
    )
  )
```
Reference a figure by its code chunk label with the `fig:` prefix, e.g.,  Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
